---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Here are some plots

today we are making interactive plots in plotly. we'll make expamples using the NYC airbnb dataset.

```{r}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

Do some initial data cleaning/subsetting

```{r}
data("nyc_airbnb")

nyc_airbnb =
  nyc_airbnb |> 
  mutate(rating=review_scores_location/2) |> 
  select(rating, neighbourhood_group, neighbourhood, room_type, lat, long, price) |> 
  drop_na(rating) |> 
  filter(
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500
  )
```

Use plotly to make some quick plots

Scatterplot
"\n" creates new line when hover over plot datapoints
```{r}
nyc_airbnb |> 
  mutate(text_label= str_c("Price: ", price, "\nNeighborhood: ", neighbourhood)) |> 
  plot_ly(
    x = ~lat, y=~long, color= ~price, text= ~text_label,
    type= "scatter", mode= "markers", alpha=0.5
  )
```



Box plot
mutate function changes price in increasing amt
```{r}
nyc_airbnb |> 
  mutate(neighbourhood= fct_reorder(neighbourhood, price)) |> 
  plot_ly(
    x= ~neighbourhood, y= ~price, color = ~neighbourhood,
    type= "box", colors = "viridis"
  )
```

Bar chart with number of rentals.
```{r}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(
    x= ~neighbourhood, y=~n,
    type= "bar"
  )
```

```{r}
plot_ly(
  z=volcano, type = "heatmap"
)
```

Look at plotly cheatsheat.. e.g., chloropleth




